Topological Equivariant Artist Model for Visualization Library Architecture

### 2022-04-14 paper/main.tex
testing nu and q

\subsection{Fiber Bundles}
\label{sec:atct:fiber-bundles}
Fiber bundles, are a "unified, dimension-independent framework", as described by Butler\cite{butlerVectorBundleClassesForm1992,butlerVisualizationModelBased1989}, that allow us to seperatly describe the topololigical properties and fields of a data source and also the mapping between topolology and data values. A fiber bundle $(\dtotalc, \dbasec, \pi, \dfiberc)$ is a structure with topological spaces $\dtotalc, \dfiberc, \dbasec$ and continuous surjective map $\pi: \dtotalc \rightarrow \dbasec$\cite{FiberBundle2020}.

@@

We also use fiber bundles to represent the output of a visualization algorithm, which we term the graphic but generalizes to output on any display space, such as a screen or 3D print. 
\begin{equation}
  \label{eq:atct:fb_graphic}
  \gfiberc \hookrightarrow \gtotalc \xrightarrow{\pi} \gbasec
\end{equation}
The base space \gbasec\ is a parameterization of the display area, for example the inked bounding box in cairo \cite{CairographicsOrg}. The fiber space \gfiberc\ is an abstraction of the renderer fields, for example $\{x,\,y,\,r,\,g,\,b,\,a\}$. The sections of the graphic 
\begin{equation}
  \label{eq:atct:fb_graphic_section}
  $\cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}} \coloneqq \big\{\gsectionc: \opensetgc\rightarrow \gtotalc\restriction_{\opensetgc} \; \bigm{\vert} \pi(\gsectionc(\gbasepointc)) = \gbasepointc\;for\, all\; \gbasepointc \in \opensetgc \big\}$
\end{equation}
are functions that generate different graphics, for example markers for a scatter plot, bars for a bar chart, cells of a heatmap, or pixels of an image.

@@

A sheaf is a presheaf that satisfies the locality and gluing axioms \cite{bakerMathsSheaf}. The locality axiom is that given a union of opensets $\mathscr{\opensetc} = \bigcup\limits_{i\in I} \opensetc_i$ and $\dsectionc^{a}, \dsectionc^{b} \in \sheafc(\mathscr{\opensetc})$,  if $\dsectionc^{a}\restriction_{\opensetc_i} = \dsectionc^{b}\restriction_{\opensetc_i}$ for each $\opensetc_i \in \opensetc$ then $\dsectionc^{a} = \dsectionc^{b}$. This means that two sections in a sheaf are equal when they evaluate to the same values over all open sets in a collection. The gluing axiom is that given $\dsectionc^{i} \in \sheafc(\opensetc_i)$ such that ${\dsectionc^{i}}\restriction_{\opensetc_i\cap \opensetc_j} = {\dsectionc^{j}}\restriction_{\opensetc_i \cap \opensetc_j}$ for $\opensetc_i, \opensetc_j \in \mathscr{\opensetc}$, there exists $\dsectionc \in \sheafc(\mathscr{\opensetc})$ such that $\dsectionc\restriction_{\opensetc_i} = {\dsectionc^{i}}$. This means we can construct a section $\dsection$ on the collection of open sets that is the union of sections defined on specific open sets. This expresses an equivalency between a concatenated represetation of data and the distributed represetation of the same data.

@@

\subsubsection{Measurement Types}

We specify that structure on a sheaf includes the actions $\dfuncc$ on sections of that sheaf, which is a generalization of Steven's \cite{stevensTheoryScalesMeasurement1946} classification of measurement scales by their mathematical group structure. These sheaf actions describe which changes in the data we expect to be equivariant to changes in the visualization.

@@

In this work, we assume that the map
\begin{equation}
\dfunch: \openset^{\prime}\rightarrow \openset
\end{equation}
is from one open set to another open set in the same base space $\openset, \openset^{\prime} \subseteq \dbase$. For example a remapping of an underlying indexing, such as a sorting of primary keys for a database of discrete values. This base space transfromation induces a pullback section 
\begin{equation}
  \dfuncpull \dsection \restriction_{\openset}: \dsection\restriction_{\openset} \mapsto \dsection \restriction_{\openset} \circ \dfunch 
\end{equation}
such that $\dsection|_{\openset} = \dfuncpull\dsection|_{\opensetc^{\prime}}$ because $\dsection|_{\openset} = \dsection|_{\dfunch(\opensetc^{prime})}$. This means that the base space transformation \dfunch\ alone does not change the data values.

@@

The full transformation 
\begin{equation}
  \dfunc: \dsection\restriction_{\openset} \mapsto \dsection^{\prime}\restriction_{\openset} \circ \dfunch
\end{equation}
is used to express actions such as rotation that induce both a remapping of the index space and a change in the data values. The data transform \dfunc\ is composable
\begin{equation}
  \dfuncc = (\dfunchc, \prod\limits_{i=0}^{n}\dfunctc_i)
\end{equation}
if there exists functions $\dfunc_{a,b}: \dtotal_a \times \dtotal_b \rightarrow \dtotal_a \times \dtotal_b$, $\dfunc_{a}: \dtotal_a \rightarrow \dtotal_a$ and $\dfunc_{b}: \dtotal_b \rightarrow \dtotal_b$ s.t. $\pi_a \circ \dfunc_a = \dfunc_{a,b} \circ \pi_a$ and $\pi_b \circ \dfunc_b = \dfunc_{a,b} \circ \pi_b$ then $\dfunc_{a,b} = (\dfunc_a, \dfunc_b)$. This allows us to define a data transform where each fiber transform $\dfunct_{i}$ can be applied to a different fiber field $\dfiber_i$.

\subsection{Map Between Base Spaces}
\note{add couple of sentences introducing image functors}
We define a \textcolor{functor}{functor} between the graphic and data base spaces 
\begin{equation}
  \vindexc: \opensetgc \rightarrow \opensetc 
\end{equation}
such that every $\opensetg \subseteq \gbase$ must map to a corresponding set $\openset \subset \dbase$. In doing so, we can define the pullback \vindexpullc\  and pushforward \vindexpushc\

\begin{equation}
  \label{eq:atct:morphisms:xi}
\begin{tikzcd}[row sep=huge]
  \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} 
  \arrow[rr, "\vindexpullc", maps to, color=functor] &  & 
  \cgamma{\opensetgc}{\vindexpullc\dtotalc\restriction_{\opensetgc}}                                                                                                       \\
  \opensetc 
  \arrow[d, "{\sheafc_{\dbasec, \vindexpushc \gtotalc}}", dashed, maps to, color=sheaf] 
  \arrow[u, "{\sheafc_{\dbasec, \dtotalc}}"', maps to, color=sheaf] &  & 
  \opensetgc 
  \arrow[d, "{\sheafc_{\gbasec, \gtotalc}}", maps to, color=sheaf] 
  \arrow[u, "{\sheafc_{\gbasec, \vindexpullc\dtotalc}}"', dashed, maps to, color=sheaf] 
  \arrow[ll, "\vindexc"', maps to, color=functor] \\
  \cgamma{\opensetc}{\vindexpushc\gtotalc\restriction_{\opensetc}} &  & 
  \cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}} 
  \arrow[ll, "\vindexpushc"', maps to, color=functor]                                                         
  \end{tikzcd}
\end{equation}

@@

As illustrated in \autoref{fig:atct:morphisms:sheaf}, the \note{image functors?} between sheaves are a way of expressising the bookkeeping of data in screen and graphic space and graphic in screen and graphic space.

\section{Artist: Data to Graphic}
Because $Hom_{\gbase}(\sheaf_{\gbase, \vindexpull\dtotal}, \sheaf_{\gbase,\gtotal}) = Hom_{\dbase}(\sheaf_{\dbase, \dtotal}, \sheaf_{\dbase, \vindexpush\gtotal})$

\begin{equation}
  \begin{tikzcd}
    \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} 
    \arrow[dd, "\vartistc^{\dbasec}"', color=artist] 
    \arrow[rrdd, "\vartistc", color=artist] 
    \arrow[rr, "\vindexpullc", color=functor] &  &
    \cgamma{\opensetgc}{\vindexpullc\dtotalc\restriction_{\opensetgc}} 
    \arrow[dd, "\vartistc^{\gbasec}", color=artist] \\
     & & \\
    \cgamma{\opensetc}{\vindexpushc\gtotalc\restriction_{\opensetc}} &  & 
    \cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}} 
    \arrow[ll, "\vindexpushc"', color=functor]                  
    \end{tikzcd}
\end{equation}

\begin{equation}
  \imartist{\opensetgc}{\gtotalc\restriction_{\opensetgc}} \coloneqq \{\gsectionc\vert\;\exists\;\dsectionc \in \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}}\;s.t.\; 
  \vartistc(\dsectionc) = \gsectionc,\; \vindexc(\opensetgc) = \opensetc \} 
\end{equation}
$\imartist{\opensetg}{\gtotal\restriction_{\opensetg}} \subset \cgamma{\opensetg}{\gtotal\restriction_{\opensetg}}$

\subsection{Equivariant Artist}
\begin{equation*}
  \begin{tikzcd}[ampersand replacement=\&, column sep=small]
  \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} 
  \arrow[rrr, "\vartistc", color=artist] 
  \arrow[d, "\dfuncpullc_{\dtotalc}"', color=action] 
  \& \& \& 
  \imartist{\opensetgc}{\gtotalc\restriction_{\opensetgc}} 
  \arrow[d, "\dfuncpullc_{\gtotalc}", dotted] \\
  \cgamma{\opensetc^{\prime}}{\dfuncpullc_{\dtotalc}\dtotalc\restriction_{\opensetc^{\prime}}} 
  \arrow[dd, "\dfunctc_{\dtotalc}"', color=action] \& 
  \opensetc 
   \& 
  \opensetgc 
  \arrow[l, "\vindexc"', color=functor] 
  \& 
  \imartist{\opensetgc^{\prime}}{\dfuncpullc_{\gtotalc}\gtotalc\restriction_{\opensetgc^{\prime}}} 
  \arrow[dd, "\dfunctc_{\gtotalc}", dotted, color=action] \\
  \& 
  \opensetc^{\prime} 
  \arrow[u, "\dfunchc_{\dtotalc}", color=action] 
  \& 
  \opensetgc^{\prime} 
  \arrow[l, "\vindexc"', color=functor] 
  \arrow[u, "\dfunchc_{\gtotalc}"', dotted, color=action] 
  \& \\
  \cgamma{\opensetc^{\prime}}{\dtotalc^{\prime}\restriction_{\opensetc^{\prime}}} 
  \arrow[rrr, "\vartistc^{\prime}", color=artist]  
  \& \& \& 
  \imartist{\opensetgc^{\prime}}{\gtotalc^{\prime}\restriction_{\opensetgc^{\prime}}}
  \end{tikzcd}
\end{equation*}
For all points $\gbasepointc^{\prime}\in \gbasec^{\prime}$:
\begin{equation*}
  \vartistc^{\prime}(\dfunctc_{\dtotalc}(\dsectionc(\dfunchc_{\dtotalc}(\vindexc(\gbasepointc^{\prime}))))) = \dfunctc_{\gtotalc}(\vartistc(\dsectionc(\vindexc(\dfunchc_{\gtotalc}(\gbasepointc^{\prime})))))
\end{equation*}
\subsection*{Testing Equivariance}
\begin{equation*}
  \begin{tikzcd}[row sep=huge]
    \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}}
    \arrow[d, "\equivc", color=monoid]
     \arrow[rr, "\vartistc", color=artist] &  & \imartist{\opensetgc}{\gtotalc\restriction_{\opensetgc}} 
     \arrow[d, "\extractmc", color=monoid] \arrow[r, "render"] & VIZ \arrow[ld, "measure"] \\
    {Hom(\opensetc, \measurec)} \arrow[rr, "\vindexpullc", color=functor]  &  & {Hom(\opensetgc, \measurec)}   & 
    \end{tikzcd}
  \end{equation*}
  \begin{description}
      \item[input]{$\equivc: \dsectionc \mapsto (\opensetc \xrightarrow{\equivc_{\dsectionc}} \measurec)$}
      \item[output]{$\extractmc:\gsectionc \mapsto (\opensetgc \xrightarrow{\extractmc_{\gsectionc}} \measurec)$}
      \item[] $\equivc_{\dsectionc}(\dbasepointc) = \extractmc_{\gsectionc}(\gbasepointc)$ for all $\vindexc(\gbasepointc) = \dbasepointc, \dbasepointc \in \dbasec, \gbasepointc \in \gbasec$ 
  \end{description}

  \note{introduce $\phi_M$ as basis of equivariance}
\section{Construction}
\subsection{Measurable Visual Components}

\begin{equation}
  \vfiberc \hookrightarrow \vtotalc \xrightarrow{\pi} \dbasec
\end{equation}
where
\cgamma{\opensetc}{\vtotalc\restriction_{\opensetc}} \coloneqq \big\{\dsectionc: \opensetc\rightarrow \vtotalc\restriction_{\opensetc} \; \bigm{\vert} \pi(\dsectionc(\dbasepointc)) = \dbasepointc\;for\, all\; \dbasepointc \in \opensetc \big\}  
\begin{equation}

\end{equation}
\subsection{$\vindexc: \gbasec \rightarrow \dbasec$}
We define the functor $\vindex$ such that the data base space \dbase\ is a deformation retraction\cite{nlab:deformation_retract} of the graphic space $\gbase$, meaning that there is a continuous surjective mapping from every point $\dbasepoint\in\dbase$ to a point $\dbasepoint \in dbase$ . To simplify matters, in this paper, we construct the graphic space as a constant multiple of the base space such that 
\begin{equation}
  \underbrace{\opensetc\times[0,1]^{n}}_{\opensetgc} \textcolor{functor}{\xmapsto{\hspace{1em}\vindexc\hspace{1em}}} \opensetc} 
\end{equation}
\begin{equation*}
  n = \begin{cases}
    dim(\gbase) - dim(\dbase) & dim(\dbase)<dim(\gbase)\\
  0 & otherwise
  \end{cases}
\end{equation*}

\subsection{$\nu: \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} \rightarrow \cgamma{\opensetc}{\vtotalc\restriction_{\opensetc}}$}

>>>>

\subsection{Fiber Bundles}
\label{sec:atct:fiber-bundles}
Fiber bundles, are a "unified, dimension-independent framework", as described by Butler\cite{butlerVectorBundleClassesForm1992,butlerVisualizationModelBased1989}, that allow us to seperatly describe the topological properties and fields of a data source and also the mapping between topolology and data values. A fiber bundle $(\dtotalc, \dbasec, \pi, \dfiberc)$ is a structure with topological spaces $\dtotalc, \dfiberc, \dbasec$ and continuous surjective map $\pi: \dtotalc \rightarrow \dbasec$\cite{FiberBundle2020}.

@@

We also use fiber bundles to represent the output of a visualization algorithm, which we term the graphic but generalizes to output on any display space, such as a screen or 3D print. 
\begin{equation}
  \label{eq:atct:fb_graphic}
  \gfiberc \hookrightarrow \gtotalc \xrightarrow{\pi} \gbasec
\end{equation}
The base space \gbasec\ is a parameterization of the display area, for example the inked bounding box in cairo \cite{CairographicsOrg}. The fiber space \gfiberc\ is an abstraction of the renderer fields, for example $\{x,\,y,\,r,\,g,\,b,\,a\}$. The sections of the graphic 
\begin{equation}
  \label{eq:atct:fb_graphic_section}
  \cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}} \coloneqq \big\{\gsectionc: \opensetgc\rightarrow \gtotalc\restriction_{\opensetgc} \; \bigm{\vert} \pi(\gsectionc(\gbasepointc)) = \gbasepointc\;for\, all\; \gbasepointc \in \opensetgc \big\}
\end{equation}
are functions that generate different graphics, for example markers for a scatter plot, bars for a bar chart, cells of a heatmap, or pixels of an image.

@@

A sheaf is a presheaf that satisfies the locality and gluing axioms \cite{bakerMathsSheaf}. The locality axiom is that given a union of opensets $\mathscr{\opensetc} = \bigcup\limits_{i\in I} \opensetc_i$ and $\dsectionc^{a}, \dsectionc^{b} \in \sheafc(\mathscr{\opensetc})$,  if $\dsectionc^{a}\restriction_{\opensetc_i} = \dsectionc^{b}\restriction_{\opensetc_i}$ for each $\opensetc_i \in \opensetc$ then $\dsectionc^{a} = \dsectionc^{b}$. This means that two sections in a sheaf are equal when they evaluate to the same values over all open sets in a collection. The gluing axiom is that given $\dsectionc^{i} \in \sheafc(\opensetc_i)$ such that ${\dsectionc^{i}}\restriction_{\opensetc_i\cap \opensetc_j} = {\dsectionc^{j}}\restriction_{\opensetc_i \cap \opensetc_j}$ for $\opensetc_i, \opensetc_j \in \mathscr{\opensetc}$, there exists $\dsectionc \in \sheafc(\mathscr{\opensetc})$ such that $\dsectionc\restriction_{\opensetc_i} = {\dsectionc^{i}}$. This means we can construct a section $\dsection$ on the collection of open sets that is the union of sections defined on specific open sets. This expresses an equivalency between a concatenated represetation of data and the distributed representation of the same data.

@@

\subsubsection{Measurement Scales}
\label{sec:atct:sheaves:measurments}
We specify that structure on a sheaf includes the actions $\dfuncc$ on sections of that sheaf, which is a generalization of Steven's \cite{stevensTheoryScalesMeasurement1946} classification of measurement scales by their mathematical group structure. These sheaf actions describe which changes in the data we expect to be equivariant to changes in the visualization.

@@

In this work, we assume that the map
\begin{equation}
\dfunch: \openset^{\prime}\rightarrow \openset
\end{equation}
is from one open set to another open set in the same base space $\openset, \openset^{\prime} \subseteq \dbase$. For example a remapping of an underlying indexing, such as a sorting of primary keys for a database of discrete values. This base space transformation induces a pullback section 
\begin{equation}
  \dfuncpull \dsection \restriction_{\openset}: \dsection\restriction_{\openset} \mapsto \dsection \restriction_{\openset} \circ \dfunch 
\end{equation}
such that $\dsection|_{\openset} = \dfuncpull\dsection|_{\opensetc^{\prime}}$ because $\dsection|_{\openset} = \dsection|_{\dfunch(\opensetc^{\prime})}$. This means that the base space transformation \dfunch\ alone does not change the data values.

@@

The full transformation 
\begin{equation}
  \dfuncc: \dsectionc\restriction_{\opensetc} \mapsto \dsectionc^{\prime}\restriction_{\opensetc} \circ \dfunchc
\end{equation}
is used to express actions such as rotation that induce both a remapping of the index space and a change in the data values. The data transform \dfunc\ is composable
\begin{equation}
  \dfuncc = (\dfunchc, \prod\limits_{i=0}^{n}\dfunctc_i)
\end{equation}
if there exists functions $\dfunc_{a,b}: \dtotal_a \times \dtotal_b \rightarrow \dtotal_a \times \dtotal_b$, $\dfunc_{a}: \dtotal_a \rightarrow \dtotal_a$ and $\dfunc_{b}: \dtotal_b \rightarrow \dtotal_b$ such that $\pi_a \circ \dfunc_a = \dfunc_{a,b} \circ \pi_a$ and $\pi_b \circ \dfunc_b = \dfunc_{a,b} \circ \pi_b$ then $\dfunc_{a,b} = (\dfunc_a, \dfunc_b)$. This allows us to define a data transform where each fiber transform $\dfunct_{i}$ can be applied to a different fiber field $\dfiber_i$.

\subsection{Maps Between Spaces}
\note{add couple of sentences introducing image functors}
We propose that there must exist a continuous \textcolor{functor}{map between topological spaces} \vindexc 
\begin{equation}
  \vindexc: \opensetgc \rightarrow \opensetc 
\end{equation}
such that every $\opensetg \subseteq \gbase$ must map to a corresponding set $\openset \subset \dbase$. Given \vindex\ we can construct two functors \vindexpullc\ and \vindexpushc\ which transport sheaves

\begin{equation}
  \label{eq:atct:morphisms:xi}
\begin{tikzcd}[row sep=huge]
  \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} 
  \arrow[rr, "\vindexpullc", maps to, color=functor] &  & 
  \cgamma{\opensetgc}{\vindexpullc\dtotalc\restriction_{\opensetgc}}                                                                                                       \\
  \opensetc 
  \arrow[d, "{\sheafc_{\dbasec, \vindexpushc \gtotalc}}", dashed, maps to, color=sheaf] 
  \arrow[u, "{\sheafc_{\dbasec, \dtotalc}}"', maps to, color=sheaf] &  & 
  \opensetgc 
  \arrow[d, "{\sheafc_{\gbasec, \gtotalc}}", maps to, color=sheaf] 
  \arrow[u, "{\sheafc_{\gbasec, \vindexpullc\dtotalc}}"', dashed, maps to, color=sheaf] 
  \arrow[ll, "\vindexc"', maps to, color=functor] \\
  \cgamma{\opensetc}{\vindexpushc\gtotalc\restriction_{\opensetc}} &  & 
  \cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}} 
  \arrow[ll, "\vindexpushc"', maps to, color=functor]                                                         
  \end{tikzcd}
\end{equation}
such that $\vindexpullc$ pulls sheaves of sections on $\openset \subseteq \dbase$ over $\opensetg \subseteq \gbase$

and $\vindexpushc$ pushes sheaves of sections on $\opensetgc$ over $\openset$

The continuous map $\vindex$ and transport functors $\vindexpullc, \vindexpushc$ allow us to express the expectation that every graphic section has a corresponding data section.

@@

Functors between sheaves are a way of expressing the bookkeeping involved in keeping track of which graphic section corresponds to which data section. This allows us to construct graphic specifications for each data index $\vindexpush\gsection$ and retrieve the data $\vindexpull\dsection$ for any graphic section generating any piece of a graphic. As illustrated in \autoref{fig:atct:morphisms:sheaf}, the \note{image functors?}

We propose that visualization libraries implement morphisms from a data sheaf $\sheafc_{\dtotal, \dbase}$ to a graphic sheaf $\sheafc_{\gtotal, \gbase}$ 
\begin{equation}
  \label{eq:atct:sheaves:homset}
  \begin{tikzcd}
    \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} 
    \arrow[dd, "\textcolor{set}{Hom}_{\sheafc_{\dbasec}}"', color=homset] 
    \arrow[rrdd, "\textcolor{set}{Hom}_{\sheafc_{\dbasec},\sheafc_{\gbasec}}", color=homset] 
    \arrow[rr, "\vindexpullc", color=functor] &  &
    \cgamma{\opensetgc}{\vindexpullc\dtotalc\restriction_{\opensetgc}} 
    \arrow[dd, "\textcolor{set}{Hom}_{\sheafc_{\gbasec}}", color=homset] \\
     & & \\
    \cgamma{\opensetc}{\vindexpushc\gtotalc\restriction_{\opensetc}} &  & 
    \cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}} 
    \arrow[ll, "\vindexpushc"', color=functor]                  
    \end{tikzcd}
\end{equation}
and the hom set is the set of all morphisms from one sheaf to the other. The functors $\vindexpullc, \vindexpushc$ are adjoint, meaning that there is a functorial isomorphism \cite{harder2008lectures} such that 
\begin{equation}
\begin{split}
  & \textcolor{set}{Hom}_{\sheafc_{\gbasec}}(\vindexpullc\sheafc_{\dtotalc, \dbasec},\sheafc_{\gtotalc,\gbasec})\\
  \simeq & \textcolor{set}{Hom}_{\sheafc_{\dbasec}}(\sheafc_{\dtotalc, \dbasec},\vindexpushc\sheafc_{\gtotalc,\gbasec}) \\
  \simeq & \textcolor{set}{Hom}_{\sheafc_{\dbasec},\sheafc_{\gbasec}}(\sheafc_{\dtotalc, \dbasec},\sheafc_{\gtotalc,\gbasec}) \\
\end{split} 
\end{equation}
which means that the diagram of sheaf morphisms \autoref{eq:atct:sheaves:homset} is commutative; therefore the functors $\vindexpullc$ and $\vindexpushc$ can be used to adapt morphisms written over one space to another space. This provides us flexibility over which space to construct data to graphic transforms. For example, specifications such as svg\cite{quintScalable2003} and Vega\cite{satyanarayanDeclarativeInteractionDesign2014}, typically define their transformations in data space and return specifications for the render to evaluate. It may also be 
An artist may also want to specify the transformations in a proxy of graphic space, for example for operations like dynamic resampling \note{citation:root maybe}.

\section{Artist: Data to Graphic}
\label{sec:artist}
In this work we propose that visualization libraries are implementing a subset of the functions in the hom sets in \autoref{eq:atct:sheaves:homset} and we call these subset of functions the artist:
\begin{align}
  \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} &\textcolor{artist}{\xrightarrow{\vartistc}} \cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}} &\in \textcolor{set}{Hom}_{\sheafc_{\dbase}, \sheafc_{\gbase}}\\
  \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} &\textcolor{artist}{\xrightarrow{\vartistc^{\dbasec}}} \cgamma{\opensetc}{\vindexpushc\gtotalc\restriction_{\opensetc}} &\in \textcolor{set}{Hom}{\sheafc_{\dbase}}\\
  \cgamma{\opensetgc}{\vindexpullc\dtotalc\restriction_{\opensetgc}} &\textcolor{artist}{\xrightarrow{\vartistc^{\gbasec}}} \cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}} &\in \textcolor{set}{Hom}_{\sheafc_{\gbase}}\\
\end{align}

The space of all sections $\cgamma{\opensetg}{\gtotal\restriction_{\openset}}$ includes sections that may not be structure preserving. For example, a section may go from every point in the graphic space to the same single point in the graphic fiber $\gsection(\gbasepoint_i) = d\; \forall \gbasepoint \in \gbase$ such that the visual output is a single inked pixel on a screen.

The output of an artist \vartist\ is a restricted subset of graphic sections
\begin{equation}
  \imartist{\opensetgc}{\gtotalc\restriction_{\opensetgc}} \coloneqq \{\gsectionc\vert\;\exists\;\dsectionc \in \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}}\;s.t.\; 
  \vartistc(\dsectionc) = \gsectionc,\; \vindexc(\opensetgc) = \opensetc \} 
\end{equation} that are by definition only reachable through a structure preserving artist, which we describe in \autoref{sec:artist:equivariance}.

\subsection*{Equivariance}
\label{sec:artist:equivariance}
\begin{equation*}
  \begin{tikzcd}[ampersand replacement=\&, column sep=small]
  \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} 
  \arrow[rrr, "\vartistc", color=artist] 
  \arrow[d, "\dfuncpullc_{\dtotalc}"', color=action] 
  \& \& \& 
  \imartist{\opensetgc}{\gtotalc\restriction_{\opensetgc}} 
  \arrow[d, "\dfuncpullc_{\gtotalc}", dotted] \\
  \cgamma{\opensetc^{\prime}}{\dfuncpullc_{\dtotalc}\dtotalc\restriction_{\opensetc^{\prime}}} 
  \arrow[dd, "\dfunctc_{\dtotalc}"', color=action] \& 
  \opensetc 
   \& 
  \opensetgc 
  \arrow[l, "\vindexc"', color=functor] 
  \& 
  \imartist{\opensetgc^{\prime}}{\dfuncpullc_{\gtotalc}\gtotalc\restriction_{\opensetgc^{\prime}}} 
  \arrow[dd, "\dfunctc_{\gtotalc}", dotted, color=action] \\
  \& 
  \opensetc^{\prime} 
  \arrow[u, "\dfunchc_{\dtotalc}", color=action] 
  \& 
  \opensetgc^{\prime} 
  \arrow[l, "\vindexc"', color=functor] 
  \arrow[u, "\dfunchc_{\gtotalc}"', dotted, color=action] 
  \& \\
  \cgamma{\opensetc^{\prime}}{\dtotalc^{\prime}\restriction_{\opensetc^{\prime}}} 
  \arrow[rrr, "\vartistc^{\prime}", color=artist]  
  \& \& \& 
  \imartist{\opensetgc^{\prime}}{\gtotalc^{\prime}\restriction_{\opensetgc^{\prime}}}
  \end{tikzcd}
\end{equation*}
For all points $\gbasepointc^{\prime}\in \gbasec^{\prime}$:
\begin{equation*}
  \vartistc^{\prime}(\dfunctc_{\dtotalc}(\dsectionc(\dfunchc_{\dtotalc}(\vindexc(\gbasepointc^{\prime}))))) = \dfunctc_{\gtotalc}(\vartistc(\dsectionc(\vindexc(\dfunchc_{\gtotalc}(\gbasepointc^{\prime})))))
\end{equation*}

\subsection*{Testing Equivariance}
\begin{equation*}
  \begin{tikzcd}[row sep=huge]
    \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}}
    \arrow[d, "\equivc", color=monoid]
     \arrow[rr, "\vartistc", color=artist] &  & \imartist{\opensetgc}{\gtotalc\restriction_{\opensetgc}} 
     \arrow[d, "\extractmc", color=monoid] \arrow[r, "render"] & VIZ \arrow[ld, "measure"] \\
    {Hom(\opensetc, \measurec)} \arrow[rr, "\vindexpullc", color=functor]  &  & {Hom(\opensetgc, \measurec)}   & 
    \end{tikzcd}
  \end{equation*}
  \begin{description}
      \item[expected]{$\equivc: \dsectionc \mapsto (\opensetc \xrightarrow{\equivc_{\dsectionc}} \measurec)$}
      \item[actual]{$\extractmc:\gsectionc \mapsto (\opensetgc \xrightarrow{\extractmc_{\gsectionc}} \measurec)$}
      \item[] $\equivc_{\dsectionc}(\dbasepointc) = \extractmc_{\gsectionc}(\gbasepointc)$ for all $\vindexc(\gbasepointc) = \dbasepointc, \dbasepointc \in \dbasec, \gbasepointc \in \gbasec$ 
  \end{description}

  \note{introduce $\phi_M$ as basis of equivariance}

\section{Construction}
\label{sec:construction}
\subsection{Measurable Visual Components}

\begin{equation}
  \vfiberc \hookrightarrow \vtotalc \xrightarrow{\pi} \dbasec
\end{equation}
where
\begin{equation}
\cgamma{\opensetc}{\vtotalc\restriction_{\opensetc}} \coloneqq \big\{\vsectionc: \opensetc\rightarrow \vtotalc\restriction_{\opensetc} \; \bigm{\vert} \pi(\vsectionc(\dbasepointc)) = \dbasepointc\;for\, all\; \dbasepointc \in \opensetc \big\} 
\end{equation}

The bundle $\vtotal$ is structurally equivalent to the bundle $\dtotal$, but allows for separating the data that is input into the artist $\dsection$ from the data internal to the artist $\vsection$. This separation also allows for defining many of the target measurements \measure\ and the equivariant transformations to the measurements as internal components of the artists.

\subsection{$\vindexc: \gbasec \rightarrow \dbasec$}
We define the functor $\vindex$ such that the data base space \dbase\ is a deformation retraction\cite{nlab:deformation_retract} of the graphic space $\gbase$, meaning that there is a continuous surjective mapping from every point $\dbasepoint\in\dbase$ to a point $\dbasepoint \in dbase$ . To simplify matters, in this paper, we construct the graphic space as a constant multiple of the base space such that 
\begin{equation}
  \underbrace{\opensetc\times[0,1]^{n}}_{\opensetgc} \textcolor{functor}{\xmapsto{\hspace{1em}\vindexc\hspace{1em}}} \opensetc} 
\end{equation}
\begin{equation*}
  n = \begin{cases}
    dim(\gbase) - dim(\dbase) & dim(\dbase)<dim(\gbase)\\
  0 & otherwise
  \end{cases}
\end{equation*}

\subsection{$\nu: \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}} \rightarrow \cgamma{\opensetc}{\vtotalc\restriction_{\opensetc}}$}
The transformation $\vchannel$ is a pointwise transformation $\pi(\dtotal) = \pi(\vchannel(\dtotal))$ such that 
\begin{equation}
  \label{eq:constrution:nu}
  \vchannelc: \dfiberc_{\dfiberc} \rightarrow \vfiberc_{\dbasepoint}
\end{equation}
which means that every point in a data fiber $\delement \in \dfiber_{\dbasepointc}$ can be mapped into a correspoindg point in the visual fiber $\velement \in \vfiber_{\dbasepointc}$. A pair of transformations $(\vchannel, \vchannel^{\prime})$ are equivariant if 
\begin{equation}
  \dfunct_{\vtotal} \vchannel(\dsection(\dbasepoint)) = \vchannel^{\prime}(\dfunct_{\dtotal}(\dsection(\dbasepoint)))\; \forall \dbasepoint \in \dbase
\end{equation}
and a transformation $\vchannel$ is equivariant when $\vchannel = \vchannel^{\prime}$
\subsection*{Compositing \vchannelc's}

\begin{equation}
  \begin{tikzcd}[col sep=Huge]
    \dfiberc_{\dbasepointc} 
    \arrow[rr, "\vchannelc", color=artist] 
    \arrow[rrrr, "\vchannelc^{\prime\prime}", dashed, bend right, color=artist] &  & 
    \vfiberc_{\dbasepointc}\coloneqq{\dfiberc_{\dbasepointc}^{\prime}} 
    \arrow[rr, "\vchannelc^{\prime}", color=artist] &  & 
    \vfiberc^{\prime}_{\dbasepointc}
  \end{tikzcd}
\end{equation}
